{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2024-12-30 Notebook LaTEX/Proposal/main.tex
>w<, changess

            \todo{$\blacksquare$ Add bib \\ $\square$ Cite. }\hl{Pang, Cui's book}

@@

            \todo{$\blacksquare$ Add bib \\ $\square$ Cite. }\hl{Pang, Cui's book}

@@

        \todo{$\blacksquare$ Add Guler's 1992 new proximal point paper. \\ $\square$ Cite it. }
        {\hl{Güler}} 

@@

        \todo{$\blacksquare$ Add the paper: ``Accelerating the cubic regularization of Newton’s method on convex
        problems''\\ $\square$ Cite it.}
        {\hl{Nesterov}}

@@

        \todo{$\blacksquare$ Cite it. }\hl{(6.1.19) of Nesterov's book }\cite{nesterov_lectures_2018}, it's also used to derive a method of accelerated mirror descent. 

@@

        \todo{$\blacksquare$ Add paper: ``Accelerated regularized newton methods for minimizing composite convex functions'' \\ $\square$ Cite it. }
        {\hl{Geovani N. et al}}
        used the technique to derive a accelerated Newton's method for convex composite objective function. 

@@

    \todo{$\blacksquare$ Add Nesterov's original paper. \\ $\square$ Cite it.  }
    {\hl{Proposed back in 1983 the original Nesterov's acceleration method}} 

@@

    \todo{$\blacksquare$ Add Nesterov's new book. \\ $\blacksquare$ Cite it.}

@@

    \todo{$\blacksquare$ Add Beck 2009 FISTA original paper. $\square$ Cite it.}
    {\hl{Beck and Toubelle}} 

@@

        $\square$ Cite Section 5.2.2 for the former, cite the entirety for the later. 

@@

    {\hl{See} (5.2.2) Necoara et al. and Aujol et al. } 

@@

        $\blacksquare$ Add Neol J. Walkington's ``Nesterov's Method for Convex  Optimization''. \\ $\square$ Cite it. 

@@

        \\ $\square$ Cite it. }

@@

        The same variant also appears in Beck's book as V-FISTA, and Nesterov's book as (2.2.22).

@@

        \\ $\square$ Cite them. }
    {\hl{Chambolle, Dossal}} 

@@

            $\blacksquare$ Add ``On the convergence of the iterates of...'' \\ $\square$ Cite them.}
        {\hl{Chambolle, Dossal}}, 

@@

            $\blacksquare$ Add beck's original FISTA Paper. \\$\square$ Cite it.

@@

        {\hl{Beck}}. 

@@

        Organization now follows. 
        Section \ref{ssec:building-block-rwapg} provides a stepwise description of the R-WAPG iterative algorithm along with an inequality crucial to proving the convergence rate later. 
        Section \ref{ssec:rwpag-seq-and-alg} introduce the definition of an R-WAPG sequence, which constraints all possible parameters used permitted by the algorithm.
        The section also states the full R-WAPG algorithm and an upper bound on $F(x_k) - F(x^*)$. 
        Here, $x_k$ is generated by the R-WAPG algorithm and $x^*$ is the minimizer. 
        Section \ref{ssec:quiv-repr-rwapg} bring forward three equivalent forms of the R-WAPG algorithm making it more comparable with other Accelerated Proximal Gradient method appeared in the literatures. 
        Section \ref{ssec:describe-variants-with-rwapg} gives characterizations of specific R-WAPG sequence that leads to convergence of the R-WAPG algorithm in terms of the optimality gap. 
        The section also identifies specific instance of permissible R-WAPG sequences where it fits with the FISTA, V-FISTA, and the algorithm proposed by 
        \todo{$\square$ Cite the Chambolle, Dossal 2015 paper here again. }
        {\hl{Chambolle Dossal}}.

@@

        \todo{$\square$ Add and explain this part. }{\hl{

@@

            \todo{$\blacksquare$ Add them \\ $\square$ Cite them. }

@@

            \todo{$\square$ Cite Chambolle Dossal 2015 again. }

@@

    \subsection{The descriptive power of R-WAPG on existing variants}\label{ssec:describe-variants-with-rwapg}
        \todoinline{\noindent
            Lemmas: 
            \begin{enumerate}
                \item Inverted FISTA sequence is a R-WAPG sequence.
                \item Constant R-WAPG sequence.
            \end{enumerate}
            Theorems: 
            \begin{enumerate}
                \item Convergence with constant momentum. 
                \item Convergence with Chambolle, Dossal Sequences.
            \end{enumerate}
            Todo: 
            \begin{enumerate}
                \item Explain what is what. 
            \end{enumerate}
        }
        Lemma \ref{lemma:inverted-fista-seq} indentifies a sequence $(\alpha_k)_{k \ge 0}$ such that $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}$ as an specific instance of R-WAPG sequence. 
        The lemma showed that sequence $(\alpha_k^{-1})_{k \ge 0}$ is the FISTA sequence which governs the momentum term and convergence claim in FISTA algorithms and variants alike. 
        The lemma also provides a simplified convergence claim using the R-WAPG sequence on Proposition \ref{prop:wagp-convergence}. 
        Theorem \ref{thm:r-wapg-on-cham-doss} stated that the sequences given in  
        \todo{$\square$ Cite this paper again here. }{\hl{Chambolle, Dossal's}}
        paper indeed is an instance of R-WAPG sequence, along with that, it indeed attains a convergence rate $\mathcal O(1/k^2)$. 
        \par

@@

\section{Catalyst accelerations and future works}\label{sec:catalyst}
    \todoinline{\noindent
        Literatures review of the topics in Catalyst acceleration method. 
        Here is a list of topics: 
        \begin{enumerate}
            \item The original accelerated PPM. 
            \item The Catalyst with weakly convex objectives. 
        \end{enumerate}
        After the literature reviews of the core literatures, move on and state new research directions and open problems. 
        There are several directions for open problem: 
        \begin{enumerate}
            \item APPM method for monotone operators instead of just subgradient, whether the same framework exists in a greater context. 
            \item Accelerated Proximal Bregman Method. 
            \item Removing smoothness assumption in Catalyst acceleration framework. 
        \end{enumerate}  
    }
    \todoinline{\noindent
        A list of relevant literatures: 
        \begin{enumerate}
            \item Güler's 1992 paper on Accelerated Proximal Point method. 
            \item Lin's, and Payquette's three triology paper on Catalyst acceleration for convex, non-convex Variance reduced algorithm. 
        \end{enumerate}
    }

>>>>

            \todo{$\blacksquare$ Add bib \\ $\blacksquare$ Cite. }
            \hl{Pang, Cui's book} \cite{ying_modern_2021}

@@

            \todo{$\blacksquare$ Add bib \\ $\blacksquare$ Cite. }
            {\hl{Pang, Cui's book}} \cite{ying_modern_2021}

@@

            $\blacksquare$ Add Guler's 1992 new proximal point paper. 
            \\ $\blacksquare$ Cite it.}
        {\hl{Güler}} \cite{guler_new_1992}

@@

            $\blacksquare$ Add the paper: ``Accelerating the cubic regularization of Newton’s method on convex
            problems''\\ 
            $\blacksquare$ Cite it.
        {\hl{Nesterov}} \cite{nesterov_accelerating_2008}

@@

            $\blacksquare$ Cite it. 
        \hl{(6.1.19) of Nesterov's book }\cite{nesterov_lectures_2018}, 
        it's also used to derive a method of accelerated mirror descent. 

@@

            $\blacksquare$ Add paper: ``Accelerated regularized newton methods for minimizing composite convex functions'' \\ 
            $\blacksquare$ Cite it. 
        {\hl{Geovani N. et al}} \cite{grapiglia_accelerated_2019}
        used the technique to derive an accelerated Newton's method for convex composite objective function. 

@@

        $\blacksquare$ Add Nesterov's original paper. \\ 
        $\blacksquare$ Cite it.  
    {\hl{Proposed back in 1983 the original Nesterov's acceleration method}} \cite{nesterov_method_1983}

@@

        $\blacksquare$ Add Nesterov's new book. 
        \\ $\blacksquare$ Cite it.

@@

        $\blacksquare$ Add Beck 2009 FISTA original paper. \\
        $\blacksquare$ Cite it.
    {\hl{Beck and Toubelle}} \cite{beck_fast_2009}

@@

        $\blacksquare$ Cite Section 5.2.2 for the former, cite the entirety for the latter. 

@@

    {\hl{See} (5.2.2) Necoara et al. \cite{necoara_linear_2019} and Aujol et al. \cite{aujol_parameter-free_2024}}

@@

        $\blacksquare$ Add Neol J. Walkington's ``Nesterov's Method for Convex  Optimization''. \\ 
        $\blacksquare$ Cite it. 

@@

        \\ $\blacksquare$ Cite it. }

@@

        The same variant also appears in Beck's book as V-FISTA} \cite{beck_first-order_2017}, and \hl{Nesterov's book as (2.2.22)} \cite{nesterov_lectures_2018}.

@@

        $\blacksquare$ Cite them. }
    {\hl{Chambolle, Dossal}} \cite{chambolle_convergence_2015}

@@

            $\blacksquare$ Add ``On the convergence of the iterates of...'' \\ $\blacksquare$ Cite them.}
        {\hl{Chambolle, Dossal}} \cite{chambolle_convergence_2015},

@@

            $\blacksquare$ Add beck's original FISTA Paper. 
            \\$\blacksquare$ Cite it.

@@

        {\hl{Beck}} \cite{beck_fast_2009}.

@@

        Organization now follows. 
        Section \ref{ssec:building-block-rwapg} provides a stepwise description of the R-WAPG iterative algorithm along with an inequality crucial to proving the convergence rate later. 
        Section \ref{ssec:rwpag-seq-and-alg} introduce the definition of an R-WAPG sequence, which constraints all possible parameters used permitted by the algorithm.
        The section also states the full R-WAPG algorithm and an upper bound on $F(x_k) - F(x^*)$. 
        Here, $x_k$ is generated by the R-WAPG algorithm and $x^*$ is the minimizer. 
        Section \ref{ssec:quiv-repr-rwapg} bring forward three equivalent forms of the R-WAPG algorithm making it more comparable with other Accelerated Proximal Gradient method appeared in the literatures. 
        Section \ref{ssec:describe-variants-with-rwapg} gives characterizations of specific R-WAPG sequence that leads to convergence of the R-WAPG algorithm in terms of the optimality gap. 
        The section also identifies specific instance of permissible R-WAPG sequences where it fits with the FISTA, V-FISTA, and the algorithm proposed by 
        \todo{
            $\blacksquare$ Cite the Chambolle, Dossal 2015 paper here again. 
        }
        {\hl{Chambolle Dossal}} \cite{chambolle_convergence_2015}.

@@

        \todo{$\blacksquare$ Add and explain this part. }{\hl{

@@

                $\blacksquare$ Add them \\ 
                $\blacksquare$ Cite them. 

@@

            \todo{$\blacksquare$ Cite Chambolle Dossal 2015 again. }

@@

    \subsection{The descriptive power of R-WAPG on existing variants}\label{ssec:describe-variants-with-rwapg}
        \todoinline{\noindent
            Lemmas: 
            \begin{enumerate}
                \item Inverted FISTA sequence is a R-WAPG sequence.
                \item Constant R-WAPG sequence.
            \end{enumerate}
            Theorems: 
            \begin{enumerate}
                \item Convergence with constant momentum. 
                \item Convergence with Chambolle, Dossal Sequences.
            \end{enumerate}
            Todo: 
            \begin{enumerate}
                \item Explain what is what. 
            \end{enumerate}
        }
        Lemma \ref{lemma:inverted-fista-seq} identifies a sequence $(\alpha_k)_{k \ge 0}$ such that $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}$ as a specific instance of R-WAPG sequence. 
        The lemma showed that sequence $(\alpha_k^{-1})_{k \ge 0}$ is the FISTA sequence which governs the momentum term and convergence claim in FISTA algorithms and variants alike. 
        The lemma also provides a simplified convergence claim using the R-WAPG sequence on Proposition \ref{prop:wagp-convergence}. 
        Theorem \ref{thm:r-wapg-on-cham-doss} stated that the sequences given in  
        \todo{$\blacksquare$ Cite this paper again here. }
        {\hl{Chambolle, Dossal's}}
        paper \cite{chambolle_convergence_2015} indeed is an instance of R-WAPG sequence, along with that, it indeed attains a convergence rate $\mathcal O(1/k^2)$. 
        \par

@@

\section{Catalyst accelerations and future works}\label{sec:catalyst}
    \todoinline{\noindent
        Literatures review of the topics in Catalyst acceleration method. 
        Here is a list of topics: 
        \begin{enumerate}
            \item The original accelerated PPM. 
            \item The Catalyst with weakly convex objectives. 
        \end{enumerate}
        After the literature reviews of the core literatures, move on and state new research directions and open problems. 
        There are several directions for open problem: 
        \begin{enumerate}
            \item APPM method for monotone operators instead of just subgradient, whether the same framework exists in a greater context. 
            \item Accelerated Proximal Bregman Method. 
            \item Removing smoothness assumption in Catalyst acceleration framework. 
        \end{enumerate}  
    }
    \todoinline{\noindent
        A list of relevant literatures: 
        \begin{enumerate}
            \item Güler's 1992 paper on Accelerated Proximal Point method. 
            \item Lin's, and Payquette's three trilogy paper on Catalyst acceleration for convex, non-convex Variance reduced algorithm. 
        \end{enumerate}
    }
